\paragraph{}
My name is Michael Fryer. I am a software developer with over 5 years of on-and-off web development experience. I am currently pursuing a Masters in Applied Data Science at Frankfurt School of Finance and Management with an expected graduation date of Summer 2027. I have previously worked at Heavy Iron Studios in Manhattan Beach, CA as an Associate Game Developer. During my tenure at Heavy Iron, I was the lead UI developer on PacMan: Mega Tunnel Battle, our UE4 game for Bandai Namco. In addition to my responsibilities on the game UI, I also created the Live Ops portal that Bandai Namco would use once the game was shipped. For that project I chose to use Django as my front-end framework of choice. After our deliverable, I was put on the Rocket League team where I briefly worked on a still unreleased project. After leaving Heavy Iron, I have been pursuing my passion for content creation. Over the course of these years, I have grown both my YouTube channel and my Twitch channel. I have additionally created technical solutions for creators. By dedicating myself to working in the content creation space, I was invited to become part of a content creation team where I would work collaboratively with other members to create entertaining content. This journey has let me develop many skills I wouldn't have otherwise. This includes video editing, image editing, project management, and leadership.

\paragraph{}
I believe I am a qualified candidate for this position as outlined in my attached resume. In addition to the skills and job experience listed in my resume, I was a part of the hiring team for Heavy Iron. As part of the hiring team, I am tasked with vetting potential candidates and testing their skills. I am currently working as a freelancer where I create tools for streamers and websites. When developing websites I have grown fond of using NextJS and TailwindCSS to speed up my development process. My most recent project was developing a website that tracks recently published videos for \href{https://arcadia.yt}{ArcadiaSMP}.