\paragraph{}
My name is Michael Fryer. I have previously worked at Heavy Iron Studios in Manhattan Beach, LA as an Associate Game Developer. During my tenure at Heavy Iron, I was the lead UI developer on PacMan: Mega Tunnel Battle. Our game was built in UE4 and delivered to Bandai Namco in the fall of 2020. In addition to my responsibilities on the game UI, I also created the Live Ops portal that Bandai Namco would use once the game was shipped. For that project, I chose to use Django as my front-end framework of choice. After our deliverable, I was put on the Rocket League team where I briefly worked on a still unreleased project. After leaving for personal reasons, I have been pursuing my passion for content creation. Over the course of these years, I have grown both my \href{https://youtube.com/@humblehominid}{YouTube} channel and my \href{https://twitch.tv/HumbleHominid}{Twitch} channel. By dedicating myself to working on content creation I was invited to become part of a content creation team where I would work collaboratively with other members to create entertaining content. This journey has let me develop many skills I wouldn't have otherwise. This includes video editing, image editing, project management, and leadership.

\paragraph{}
I believe I am a qualified candidate for this position as outlined in my attached resume. In addition to the skills and job experience listed in my resume, I am also an affiliate on \href{https://twitch.tv/HumbleHominid}{Twitch}. Over the course of the last 3 years I have grown my audience on Twitch and YouTube as a content creator. At the same time, I have been developing tools for my fellow content creators to help them in their content creation process.