\paragraph{}
My name is Michael Fryer. I have previously worked at Heavy Iron Studios in LA as an Associate Game Developer. During my tenure at Heavy Iron, I was the lead UI developer on PacMan: Mega Tunnel Battle. Our game was built in UE4 and delivered to Bandai Namco in the fall of 2020. In addition to my responsibilities on the game UI, I also created the Live Ops portal that Bandai Namco would use once the game was shipped. For that project, I chose to use Django as my front-end framework of choice. After our deliverable, I was put on the Rocket League team where I briefly worked on a still unreleased project. After leaving for personal reasons, I have been pursuing my passion for content creation. Over the course of these years, I have grown both my YouTube channel and my Twitch channel. By dedicating myself to working on content creation I was invited to become part of a content creation team where I would work collaboratively with other members to create entertaining content. This journey has let me develop many skills I wouldn't have otherwise. This includes video editing, image editing, project management, and leadership.

\paragraph{}
I believe I am a qualified candidate for this position as outlined in my attached resume. In addition to the skills and job experience listed in my resume, I was a part of the hiring team for Heavy Iron. As part of the hiring team, I am tasked with vetting potential candidates and testing their skills. Before my time at Heavy Iron, I held leadership positions as the secretary and club president for Montana Tech's student chapter of ACM. As secretary, I was a lead proponent for getting my school recognized as an official testing facility for the regional ICPC programming competition. By becoming a regional testing facility, Montana Tech was able to invite many schools from Montana to participate in the competition when they wouldn't normally have had the opportunity since the next closest testing facility is in Colorado.