July 16, 2019\\
\mbox{}\\

To Whom it may Concern,
\paragraph{}
My name is Michael Fryer, and I found your \textit{Game Services Engineer} position listed at \href{https://www.linkedin.com/jobs/view/1315865563/?refId=154ee4fc-6fe7-4709-9fcb-49e5ac42662a&trk=flagship3_search_srp_jobs}{linkedin}. I am a recent college graduate from Montana Tech's ABET accredited Computer Science and Software Engineering programs with a Bachelors in Computer Science with a Game Design option and a Bachelors in Software Engineering. I am currently working under contract with the Butte Foodbank to continue the development of my senior project, Food Resources Expenses, and Distribution, or FRED, as well as to maintain the application once it is completed.\\

\paragraph{}
Your position position mentions a need for someone who is interested in games and has a desire to learn. I fit into that category. I have played games ever since I was a kid when Halo came out on the very first xbox. Ever since then I have developed a passion for video games even stating in my middle school year book that my dream job would be to "Be a video game maker." Aside from dreams and passions, I developed experience with C\# and MySQL when I worked of FRED for my senior design project. Started as a Senior Design project in 2017, FRED was continued by my team and me got a minimum viable product deployed at the end of the 2019 school year. After the school semester ended I was offered a contract position to the Butte Foodbank to finish implementing the remaining features and maintain the application once it is completely deployed. I also have a bit of experience with AWS and EC2. I used an EC2 instance to deploy my website, \href{http://mfryer.us}{mfryer.us}, which was built using the JavaScript framework Emberjs.

\paragraph{}
My experience with C\# and JavaScript means I can quickly integrate into available teams. My passion to work in the video games industry means I will always be driven to learn more about the industry I care so much about.