\paragraph{}
My name is Michael Fryer and I heard about your open \href{https://digitalglobe.wd1.myworkdayjobs.com/en-US/MAXAR/job/Westminster-CO/Software-Development-Engineer_R09895?utm_source=Maxar-careers&utm_medium=website#path=}{Software Development Engineer} position. I have been working for Heavy Iron Studios Inc. for the last year. Before working at Heavy Iron I graduated from Montana Tech's ABET accredited Computer Science and Software Engineering programs with a Bachelors in Computer Science and Software Engineering.

\paragraph{}
I believe I am a qualified candidate for this position as outlined in my attached resume. In addition to the skills and job experience listed in my resume, I have become a part of the hiring team for Heavy Iron. As part of the hiring team, I am tasked with vetting potential candidates and testing their skills. Before my time at Heavy Iron, I held leadership positions as the secretary and club president for Montana Tech's student chapter of ACM. As secretary, I was a lead proponent for getting my school recognized as an official testing facility for the reginal ICPC programming competition. By becoming a regional testing facility, Montana Tech was able to invite many schools from Montana to participate in the competition when they wouldn't normally have had the opportunity since the next closest testing facility is in Colorado. Having been introduced to Test Driven Development during schooling and serving as the SCRUM master for my senior design project, I have hands on experience with developing rapid prototypes.