\paragraph{}
My name is Michael Fryer and I heard about your open \textit{Web Engineer} position. I am a recent college graduate from Montana Tech's ABET accredited Computer Science and Software Engineering programs with a Bachelors in Computer Science and Software Engineering. I am currently working as a contractor for the Butte Emergency Food Bank.

\paragraph{}
I believe I am a qualified candidate for this position as outlined in my attached resume. In addition to the skills and job experience listed in my resume, I have held leadership positions as the secretary and club president for Montana Tech's student chapter of ACM. As secretary, I was a lead proponent for getting my school recognized as an official testing facility for the reginal ICPC programming competition. By becoming a regional testing facility, Montana Tech was able to invite many schools from Montana to participate in the competition when they wouldn't normally have had the opportunity since the next closest testing facility is in Colorado. Having been introduced to Test Driven Development during schooling and serving as the SCRUM master for my senior design project, I have hands on experience with developing rapid prototypes. Although not on my resume, I have had experience with ffmpeg in one of my summer internships. I was tasked with converting sections of mkv files into webm files for bandwidth reasons and that was accomplished with ffmpeg.

\paragraph{}
I have a passion for games and streaming as well. I like to watch streams in my spare time and I have picked up on what features help streamers interact with their chat. Additionally, I will occasionally stream for my friends or a wider audience on twitch.