July 16, 2019\\
\mbox{}\\

To Whom it may Concern,
\paragraph{}
My name is Michael Fryer, and I found your \textit{Junior Developer} position listed at \href{https://www.linkedin.com/jobs/view/1334202574/?refId=5c098f22-0d82-4248-882b-ecd249dd6353&trk=flagship3_search_srp_jobs}{linkedin}. I am a recent college graduate from Montana Tech's ABET accredited Computer Science and Software Engineering programs with a Bachelors in Computer Science and a Bachelors in Software Engineering. I am currently working under contract with the Butte Food Bank to continue the development of my senior project, Food Resources Expenses, and Distribution, or FRED, as well as to maintain the application once it is completed.\\

\paragraph{}
Your job position mentions a need for someone who has experience with .NET C\# and WPF, which is what FRED is written in. During FRED's development I learned a lot about WPF and how WPF interacts with a SQL Server backend. The position also mentions a need for someone with knowledge of JavaScript and CSS Frameworks, which I have demonstrable knowledge of on my website, \href{http://mfryer.us}{mfryer.us}, which is built using Emberjs and Bootstrap v4. The website is run on an AWS instance with a small expressjs server for serving up the blog posts. In addition to working as a scrum master for my Senior Design team, I served as the Secretary and President for my school's student chapter of ACM in 2018 and 2019. As the Secretary I worked together with the president to get our school listed as an official regional testing site for the International Collegiate Programming Competition, the ICPC. With the next closest testing site being in Denver, Colorado, having a testing site in Montana meant we were able to invite students from other programs across Montana to participate in an ICPC where they normal wouldn't have been able to due to the cost of travel.

\paragraph{}
My experience working on FRED and past projects involving Emberjs as helped me develop a deeper understanding of them both. The past experience with WPF, JavaScript frameworks, CSS frameworks, and leaderships positions will make it easy for me to get up to speed in any team I get put in.