August 13, 2019\\
\mbox{}\\
12333 W. Olympic Blvd\\
Los Angeles CA 90064\\

\paragraph{}
My name is Michael Fryer and I heard about your open \textit{Senior Software Engineer (Frontend) - League of Legends, Core Tech} position listed on your \href{https://www.riotgames.com/en/work-with-us/job/1751728}{jobs} page. I am a recent college graduate from Montana Tech's ABET accredited Computer Science and Software Engineering programs with a Bachelors in Computer Science with a Game Design Option and Software Engineering. I am currently working as a contractor for the Butte Emergency Food Bank. In my spare time I have been playing League, TFT, and watching the LEC/LCS.//

\paragraph{}
I believe I am a qualified candidate for this position as outlined in my attached resume. In addition to the skills and job experience listed in my resume, I have held leadership positions as the secretary and club president for Montana Tech's student chapter of ACM. As secretary, I was a lead proponent for getting my school recognized as an official testing facility for the reginal ICPC programming competition. By becoming a regional testing facility, Montana Tech was able to invite many schools from Montana to participate in the competition when they wouldn't normally have had the opportunity since the next closest testing facility is in Colorado. Having been introduced to Test Driven Development during schooling and serving as the SCRUM master for my senior design project, I have the experience to easily integrate into Rubicon's Test Driven Development cycle.