\paragraph{}
My name is Michael Fryer and I heard about your open position for a Software Development Engineer via Indeed. I previously worked at Heavy Iron Studios in LA for nearly two years. During those two year, I was the lead UI developer on the game we shipped. In addition to my responsibilities on the game UI, I also created the Dev Ops portal that the client would use once the game was shipped. After leaving for personal reasons, I have been pursuing my passion for content creation. Over the course of these years, I have grown both my YouTube channel and my Twitch channel. Recently, I have just elevated my Twitch channel, \href{https://twitch.tv/HumbleHominid}{HumbleHominid}, to Affiliate status which is an accomplishment I am very proud of. By dedicating myself to working on content creation I was invited to become part of a content creation team where I would work collaboratively with other members to create entertaining content. This journey has let me develop many skills I wouldn't have otherwise. This includes video editing, image editing, project management, and leadership.

\paragraph{}
I believe I am a qualified candidate for this position as outlined in my attached resume. In addition to the skills and job experience listed in my resume, I was a part of the hiring team for Heavy Iron. As part of the hiring team, I am tasked with vetting potential candidates and testing their skills. Before my time at Heavy Iron, I held leadership positions as the secretary and club president for Montana Tech's student chapter of ACM. As secretary, I was a lead proponent for getting my school recognized as an official testing facility for the regional ICPC programming competition. By becoming a regional testing facility, Montana Tech was able to invite many schools from Montana to participate in the competition when they wouldn't normally have had the opportunity since the next closest testing facility is in Colorado.